Sketch of DP - Bayesian Inference

### 2018-07-14 main-sketch.tex
updates bib

  Bayesian inference is a statistical method which allows to derive
  a \emph{posterior} distribution over a parameter, 
  starting from a \emph{prior} distribution and observed data.
  Many works have focused on making this
  process differentially private adding noise on the parameters
  representing the distributions\todo{cite?}.
  % Also,  the sensitivity 
  % was computed w.r.t. a numeric norm over the space of the numeric parameters
  % characterizing the output distribution.
  Also, the accuracy was measured
  using metrics on the space of the numeric parameters representing the
  posterior distribution, e.g. $\ell_1$-norm \todo{cite}.

>>>>

  Bayesian inference is a statistical method which allows to derive
  a \emph{posterior} distribution over a parameter, 
  starting from a \emph{prior} distribution and observed data.
  Many works have focused on making this
  process differentially private adding noise on the parameters
  representing the distributions\cite{zhang2016differential}.
  % Also,  the sensitivity 
  % was computed w.r.t. a numeric norm over the space of the numeric parameters
  % characterizing the output distribution.
  Also, the accuracy was measured
  using metrics on the space of the numeric parameters representing the
  posterior distribution, e.g. $\ell_1$-norm \cite{foulds2016theory}.
